Improvements of Chatbot-Applications offering Cognitive Behavioural Therapy regarding Efficacy, Privacy and Safety

### 2021-06-01 paper.tex
fixed typos

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
While chatbot-applications in general have become present in areas such as consulting or customer support, they are also implemented
within applications offering Cognitive Behavioural Therapy (CBT). CBT aims to improve a patients mood by changing behavioural patterns and proposing
activities that can help to achieve a higher mindfullness.
\\
Two state-of-the-art chatbots have been reviewed regarding aspects of safety, privacy and efficacy. The review has shown, that they have a positive 
impact on a users mood, take care of sensitive data and can react to critical situations but also have several weaknesses that should be addressed.
\\
As chatbots for mental health belong to Human Computer Interaction (HCI), certain requirements have been reviewed that an application in this field should meet. This review has shown
that users trust high-quality chatbots with sophisticated responses more while having less privacy concerns at the same time. Furthermore, the deletion and 
inappropriate use of data are the two aspects, users worry about the most. 
\\
Based on the review of the existing chatbots and the requirements, three development approaches have been proposed who aim to meet them.
The Knowledge and Data Dashboard, that constantly allow access to saved data and offers options like data deletion, 
the Chatbot Setup Phase that try to personalize the application as much as possible to improve the general user experience and 
a privacy certificate, that ensures the appropriate handling of critical situations.   
\end{abstract}

@@

  Talking about senstive topics is one core aspect of CBT. It results in senstive data which is processed by the application. Hence it is crucial to focus on privacy aspects.

@@

DBT is a special type of CBT and focuses more on the way a patient deals with emotions and is suitable for patients with self-destructive behaviours. Common techniques are practicing mindfullness or 

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
While chatbot-applications in general have become present in areas such as consulting or customer support, they are also implemented
within applications offering Cognitive Behavioural Therapy (CBT). CBT aims to improve a patients mood by changing behavioural patterns and proposing
activities that can help to achieve a higher mindfulness.
\\
Two state-of-the-art chatbots have been reviewed regarding aspects of safety, privacy and efficacy. The review has shown, that they have a positive 
impact on a users mood, take care of sensitive data and can react to critical situations but also have several weaknesses that should be addressed.
\\
As chatbots for mental health belong to Human Computer Interaction (HCI), certain requirements have been reviewed that an application in this field should meet. This review has shown
that users trust high-quality chatbots with sophisticated responses more while having less privacy concerns at the same time. Furthermore, the deletion and 
inappropriate use of data are the two aspects, users worry about the most. 
\\
Based on the review of the existing chatbots and the requirements, three development approaches have been proposed who aim to meet them.
The Knowledge and Data Dashboard, that constantly allow access to saved data and offers options like data deletion, 
the Chatbot Setup Phase trying to personalize the application as much as possible to improve the general user experience and 
a privacy certificate, that ensures the appropriate handling of critical situations.   
\end{abstract}

@@

  Talking about private topics is one core aspect of CBT. It results in sensitive data which is processed by the application. Hence it is crucial to focus on privacy aspects.

@@

DBT is a special type of CBT and focuses more on the way a patient deals with emotions and is suitable for patients with self-destructive behaviours. Common techniques are practicing mindfulness or 
